Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-09-20 fib2.tex
more wordsmithing

Such an embedding $c : [0, 1] \to D$ with $c(0), c(1) \in \partial D$
and touching all holes in $D_n$ we call a \emph{curve diagram}~\cite{Dehornoy2002}.

@@

Combinatorial formulation... \cite{Abramsky2007}
\begin{center}
\includegraphics[]{pic-cells.pdf}
\end{center}
Reading from the top-left corner, the words for these
two cells are $(())()$ and $()*(()).$

\section{Simulation algorithm}

Paperclip algorithm:
\begin{center}
\includegraphics[]{pic-paperclip.pdf}
\end{center}

>>>>

Such an embedding $c : [0, 1] \to D$ with $c(0), c(1) \in \partial D$
and touching all holes in $D_n$ we call a \emph{curve diagram}~\cite{Dehornoy2002},
(or just a \emph{curve} when the context is clear).

@@

The basic data structure involved in the
simulation we term a \emph{combinatorial curve
diagram.}
For each cell in the lattice,
we store a combinatorial
description of the curve intersected with that cell.
This will be insensitive to any continuous deformation of the interior of the cell,
but the simulation does not need to track any of these degrees of freedom.
\begin{center}
\includegraphics[]{pic-cells.pdf}
\end{center}
We follow essentially the same approach as taken in \cite{Abramsky2007} 
to describe elements of a Temperley-Leib algebra, but
with some extra decorations.
The key idea is to store a \emph{word} for each cell, comprised of
the letters $<$ and $>$.
When these brackets are balanced,
each such word will correspond one-to-one with an intersection
of a curve in a cell (up to any continuous deformation of the interior of the cell).
The encoding works as follows.
Reading in a clockwise direction around the edge of
the cell from the top-left corner,
we record our encouters with each piece of curve diagram,
writing a $<$ for the first encounter, and $>$ for the
second. We may also encounter a dangling piece of curve
diagram (the head or the tail), so we use another symbol $*$ for this.
The words for the above two cells will then be $<<>><>$ and $<>*<<>>.$
Getting more elaborate, we will also need to record the direction
of each piece of curve,
and we allow anyons to reside on the curve
close to the edge. (This means we cannot have more than two anyons
per piece, but if that is needed we will have added another curve diagram.)
We will also record,
for each intersection with the cell edge, which side the
intersection occurs on.

Various other consistency relations are enforced on a combinatorial curve diagram,
such as requiring two
adjacent cells to agree on their boundaries, and every curve diagram
having two ends.
(Note that in general we will have many disjoint curve diagrams.)
We also require every curve diagram to intersect 
the edges of cells transversally.
This will mean in particular that a curve will not touch a cell corner.

Two disjoint curves can be joined by...

Curves can be simplified along sections without any anyons, ...

% Each piece will have +1, +2, 0, -1, -2 right-hand turns...

% mention Jones' planar algebras ?

\section{The paperclip algorithm}

Anyons are transported around the lattice
by moving them along cell edges.
In general, such a transport will intersect with a
curve diagram in many places.
Each such intersection is transverse,
and we use each intersection point to cut
the entire transport into smaller paths each of
which touch the curve diagram twice.
%Each intersection with a curve diagram
%will then be transverse, and we
%decompose the entire path into a sequence of
%paths each of which 
%join consecutive intersections.
%Transport of an anyon can be decomposed into
%moves between adjacent components of a curve
%diagram.
The origin and destination of such an anyon path
now splits the curve diagram $c:[0, 1]\to D_n$ 
into three disjoint pieces which we term
\emph{head}, \emph{body} and \emph{tail}, where
the head contains the point $c(1)$, the tail
contains $c(0)$ and the body is the third piece.
These arise with various arrangements, but here
we focus on one instructive case, the
other cases are similar:
%We look at the particular case of moving along
%one edge of a cell,
transporting along one edge of a cell \emph{forwards} 
(from tail to head) along a curve diagram:
\begin{center}
\includegraphics[]{pic-move-anyon.pdf}
\end{center}

This arrangement is equivalent (homotopic) to one of four 
``paperclips'', which we distinguish between by counting how
many \emph{right-hand turns} are made along the body of the curve diagram.
We also show an equivalent (homotopic) picture where the
curve diagram has been straightened, and the resulting distortion
in the anyon path:
\begin{center}
\includegraphics[]{pic-paperclip.pdf}
\end{center}
The sequence of anyons along the head, body and tail, we denote as $H, B$ and $T,$
respectively.
These sequences have the same order as the underlying curve diagram, and 
we use
$H^r, B^r$ and $T^r$ to denote the same anyons with the reversed order.
Using the above diagram, we can now read off the $R$-moves for each
of the four paperclips:
\begin{align*}
-2:&\ R[B] \\
-4:&\ R[H^r] R[H] R[B] \\
+4:&\ R[B] R[T] R[T^r] \\
+6:&\ R[H^r] R[H] R[B] R[T] R[T^r] \\
\end{align*}
where notation such as $R[B]$ is understood as sequentially clockwise braiding around
each anyon in $B$.

That these four paperclips exhaust all possibilities can be seen by
considering the winding number of the simple closed curve made
by combining the body of the curve diagram with the path followed by
the anyon (appropriately reversing direction as needed).
